Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-03-29 2017-Xudong-SMT/OpenPNets-SMT.tex
Introduction finished.
Finish the introduction of the paper.

\section{Introduction}

@@

\QIN{
The pNet has developed in a series of works~\cite{HMZ:PDP15,henrio:Forte2016} and some examples has been introduced showing its ability in encoding the operators from some other algebras or the program skeletons. It is just the first step of our long-term goals. The operational semantic of the open pNet has already defined, but we only have a sketch about how to compute it and have no implementation. The operational semantic here is defined as an open automaton. The open transitions in the open automaton presenting the composition feature of the pNet is the main part of the open automaton computing and needs to satisfy several constraints. So in the computing algorithm, computing open transitions is necessary and should have some method to keep them satisfying the constraints. Then implementation of the algorithm should be finished. After getting the open automaton of the pNet, we can check the equivalence between pNets. The equivalence between pNets is "FH-bisimulation" taking the predicate of the open transitions into account each time matching such open transitions. In our long-term goals, the final target is to check the property of open systems.
}

In the nineties, several 
works extended the basic behavioral models based on labelled
transition systems to address value-passing or parameterized systems, using
various symbolic encodings of the
transitions~\cite{deSimone85,Larsen87,HennessyLin:TCS95,Linconcur96}. 
In \cite{Linconcur96}, H.M. Lin addressed value-passing calculi, for which he
developed a symbolic behavioral semantics, and proved algebraic properties.
Separately J. Rathke~\cite{HennessyRathke:TCS98} defined another
symbolic semantics for 
a parameterized broadcast calculus, together with strong and weak bisimulation
equivalences, and developed a symbolic model-checker based on a tableau
method for these processes. 30 years later, no
practical verification approach and no verification platform are
using this kind of approaches to provide proof methods for
value-passing processes or open process expressions.

\paragraph{Context}
\TODO{
  Summary of previous works on pNets and open pNets => 1/2 page.\\
  Longterm goals:\\
  - open pNets to represent operators and program skeletons (ref to
  \cite{HMZ:PDP15})\\
  - compute semantics in term of open transitions\\
  - compute equivalence (bisimulation of open automata)\\
  - model-check properties of open systems
  }
\paragraph{Contribution}
\QIN{
This paper shows that
}

\paragraph{Related works}

\TODO{say that apart from the old work by J. Rathke, we know no other
  research addressing our goals, and especially no attempts to develop
  an algorithmic treatment of such symbolic systems by interacting
  with automatic theorem provers}.

@@

>>>>

\section{Introduction}
In the nineties, several 
works extended the basic behavioral models based on labelled
transition systems to address value-passing or parameterized systems, using
various symbolic encodings of the
transitions~\cite{deSimone85,Larsen87,HennessyLin:TCS95,Linconcur96}. 
In \cite{Linconcur96}, H.M. Lin addressed value-passing calculi, for which he
developed a symbolic behavioral semantics, and proved algebraic properties.
Separately J. Rathke~\cite{HennessyRathke:TCS98} defined another
symbolic semantics for 
a parameterized broadcast calculus, together with strong and weak bisimulation
equivalences, and developed a symbolic model-checker based on a tableau
method for these processes. 30 years later, no
practical verification approach and no verification platform are
using this kind of approaches to provide proof methods for
value-passing processes or open process expressions.

\paragraph{Context}
\TODO{
  Summary of previous works on pNets and open pNets => 1/2 page.\\
  Longterm goals:\\
  - open pNets to represent operators and program skeletons (ref to
  \cite{HMZ:PDP15})\\
  - compute semantics in term of open transitions\\
  - compute equivalence (bisimulation of open automata)\\
  - model-check properties of open systems
  }

@@

\QIN{
The pNet has developed in a series of works~\cite{HMZ:PDP15,henrio:Forte2016} and some examples has been introduced showing its ability in encoding the operators from some other algebras or the program skeletons. It is just the first step of our long-term goals. The operational semantic of the open pNet has already defined, but we only have a sketch about how to compute it and have no implementation. The operational semantic here is defined as an open automaton. The open transitions in the open automaton presenting the composition feature of the pNet is the main part of the open automaton computing and needs to satisfy several constraints. So in the computing algorithm, computing open transitions is necessary and should have some method to keep them satisfying the constraints. Then implementation of the algorithm should be finished. After getting the open automaton of the pNet, we can check the equivalence between pNets. The equivalence between pNets is "FH-bisimulation" taking the predicate of the open transitions into account each time matching such open transitions. And several automatic theorem provers solver will also take part in the bisimulation checking algorithm. In our long-term goals, the final target is to check the property of open systems.
}

\paragraph{Contribution}
\QIN{
This paper presents our open automaton computing algorithm and its implementation in pNet API. Comparing the result of the algorithm with the manual result on the running example shows that the algorithm works properly in computing the open automaton for the pNet. The algorithm contains the method computing the open transitions composing the transitions from the subnets according to several defined rules the open transitions need to satisfy. These results are not the final results in fact, they still contain some unsatisfiable results we need to eliminate. To eliminate those unsatisfiability, we interact with an automatic theorem provers to use them for satisfiability checking. The translation of the pNet, mainly its presentation and its open transition predicates, is required for the implementation of the interaction.
}

\paragraph{Related works}
\TODO{say that apart from the old work by J. Rathke, we know no other
  research addressing our goals, and especially no attempts to develop
  an algorithmic treatment of such symbolic systems by interacting
  with automatic theorem provers}.

@@

\QIN{
There is not much researches try developing the symbolic bisimulation for the value-passing process algebra, as our long-term goals, especially no algorithm treatment of the symbolic systems developed by interacting with automatic theorem provers. The closest work is an old work from J. Rathke~\ref{HennessyRathke:TCS98}, who developed the symbolic bisimulaiton (both weak and strong bisimulation) on a calculus of broadcasting system (CBS). The CBS is similar with classic process calculi such as CCS, CSP, communicating by broadcasting values, one-to-many communication instead of one-to-one communication and transmitting values without blocks. That makes the definition of the symbolic semantic and bisimulation equivalence different from the classic works. 
}

\QIN{
There are many automatic theorem provers developed in previous works we can consider to use for the result pruning and bisimulation checking in our algorithm, such as Z3~\ref{}, Coq~\ref{}, Isabelle~\ref{} or Rodin~\ref{} as possible alternative. Z3 is developed by Microsoft Research based on the satisfiability modulo theories (SMT), mainly applied in extended static checking, test case generation, and predicate abstraction. Tools like Coq, Isabelle and Rodin have already integrated SMT solvers as modules for proving the theorem or formula inputed by users.
}
